Bird beak's elaboration and innovation

### 2022-02-11 Analysis/10-Figure1.Rmd
Update 10-Figure1.Rmd

pdf(file = "Figure_1a.pdf", height = 10, width = 5)
## Plot the phylo ellipse
grey_palette <- c(colour.palette(8), "grey")
par(mfrow = c(2,1), bty = "n")
plot.one.ellipse(superorder_shapespace, ID = c(1,9), colours = grey_palette, x = TRUE, y = TRUE, main = "A")
legend("topright", lwd = 5, col = grey_palette[c(1,9)], lty = 1, legend = c("Aequornithes' median variance-covariance", "Overall phylogenetic's median variance-covariance"), bg = "white")
plot.one.proj.rej(results$super_results_between, ID = 1, colours = grey_palette)
```

>>>>

pdf(file = "Figure_1a.pdf", height = 11, width = 5.5)
## Plot the phylo ellipse
grey_palette <- c(colour.palette(8), "grey")
par(mfrow = c(2,1), bty = "n")
plot.one.ellipse(superorder_shapespace, ID = c(1,9), colours = grey_palette, x = TRUE, y = TRUE, main = "A")
legend("topright", lwd = 5, col = grey_palette[c(1,9)], lty = 1, legend = c("Aequornithes' median variance-covariance", "Overall phylogenetic's median variance-covariance"), bg = "white")
plot.one.proj.rej(results$super_results_between, ID = 1, colours = grey_palette)
```
